---
title: "EDLD651 Final Project"
author: "Dillon, Eliott, Simone"
date: "11/18/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(tidyverse)
library(rio)
library(here)
library(janitor)
library(RColorBrewer)
library(gtsummary)
library(psych)
library(naniar)
library(corrplot)
library(nnet)

pew <- haven::read_sav(here("data", "Pew Research Center Global Attitudes Summer 2020 Dataset - Public.sav")) %>% clean_names() %>% as_tibble()
```


```{r DillonChunkCleaning}
DillonPew <- pew
DillonPew$country <- characterize(DillonPew$country)
DillonPew <- DillonPew %>% filter(covid_change<5)
DillonPew <- DillonPew %>% replace_with_na_all(~.x>4)
```


```{r DillonAnalysis}
CovidChangeTable <- DillonPew %>% group_by(country, covid_change) %>% summarize(n=n()) %>% mutate(freq=n/sum(n))

ggplot(CovidChangeTable, aes(x = country, y = as.numeric(freq) ,fill=as.factor(covid_change))) +
  geom_bar(stat="identity")+
  coord_flip()+
  labs(title = "'How Has Covid Changed Your Life?' by Country",
       y= "Frequency", fill="Responses")+
  scale_fill_discrete(name = "Response", labels = c("A great deal", "A fair amount", "Not too much","Not at all"))

CovidChangeMeansTable <- DillonPew %>% select(country, covid_change) %>% pivot_wider(names_from = country, values_from = covid_change, values_fn = mean) %>% pivot_longer(cols=everything())

ggplot(DillonPew, aes(x = country, y = as.numeric(covid_change) ,fill=as.factor(country))) +
  geom_boxplot()+
  coord_flip()

CovidLonger <- DillonPew %>% select(country, qs8, cregion_us) %>% filter(country=="United States" & !is.na(qs8)) %>% mutate(one = 1)
CovidLonger$qs8 <- characterize(CovidLonger$qs8)
CovidLonger$cregion_us <- characterize(CovidLonger$cregion_us) 
CovidLonger <- CovidLonger %>% pivot_wider(id_cols = c("cregion_us","qs8","one"),
                names_from = c("qs8","cregion_us"),
                values_from = "one",
                values_fn = list("one" = length))
CovidLonger <- CovidLonger %>% pivot_longer(cols=everything())

DillonCorMatrix <- cor(select(DillonPew, covid_change:covid_who) %>% select(-fav_nato, -covid_us))
parallel <- DillonCorMatrix %>% fa.parallel(., fm = 'minres', fa = 'fa', n.obs=14261)
fa.none <- fa(r=DillonCorMatrix, 
 nfactors = 7,
 n.obs=14261,
 # covar = FALSE, SMC = TRUE,
 fm="pa", # type of factor analysis we want to use (“pa” is principal axis factoring)
 max.iter=100, # (50 is the default, but we have changed it to 100
 rotate="varimax") # none rotation
print(fa.none)
KMO(r=DillonCorMatrix)
cor(select(DillonPew, covid_change:covid_who))
corrplot(DillonCorMatrix)
```

```{r}
logModel1 <- multinom(d_political_scale_us~covid_change+econ_sit,
                   data = filter(DillonPew, d_political_scale_us<5 & econ_sit<5), family = "binomial")
summary(logModel1)
coef(logModel1) %>% exp()

z <- summary(logModel1)$coefficients/summary(logModel1)$standard.errors
p <- (1 - pnorm(abs(z), 0, 1)) * 2
p
```



```{r EliottChunkCleaning}
#new df +  showing categories of interest as text
el_pew <- pew
el_pew$country <- characterize(el_pew$country)
el_pew$covid_ownfaith <- characterize(el_pew$covid_ownfaith)
el_pew$trust_people <- characterize(el_pew$trust_people)
el_pew$covid_change <- characterize(el_pew$covid_change)

#View(el_pew)

#displaying variables of interest in a table
faith_table <- el_pew %>% 
  select(covid_ownfaith, trust_people, covid_change) %>% 
  group_by(trust_people, covid_ownfaith) %>% 
  filter(trust_people == "In general, most people can be trusted" | trust_people == "In general, most people cannot be trusted",
         covid_ownfaith == "Has not changed much" | covid_ownfaith == "Stronger" | covid_ownfaith == "Weaker") %>% 
  summarize(n=n()) %>% 
  mutate(percent = (n/sum(n))*100)
faith_table

#figure
el_pew %>% 
  filter(trust_people %in% c("In general, most people can be trusted", "In general, most people cannot be trusted")) %>%
  filter(trust_people == "In general, most people can be trusted" | trust_people == "In general, most people cannot be trusted",
         covid_ownfaith == "Has not changed much" | covid_ownfaith == "Stronger" | covid_ownfaith == "Weaker",
         covid_change == "A fair amount" | covid_change == "A great deal" | covid_change == "Not at all" | covid_change == "Not too much") %>% 
  ggplot() +
  (aes(x = covid_ownfaith, fill=as.factor(covid_change))) +
  geom_bar() +
  facet_wrap(~trust_people) +
  theme_bw() +
  scale_fill_brewer(palette="RdGy") +
  labs(title = "Faith Change during COVID-19 Pandemic",
       subtitle = "by trust in people and amount of life change during the pandemic",
       x = "Faith Change",
       y = "Frequency") +
  coord_flip()

#displaying faith change with trust in people
faith_table_wider <- el_pew %>% 
  select(covid_ownfaith, covid_change, trust_people) %>% 
  filter(trust_people == "In general, most people can be trusted" | trust_people == "In general, most people cannot be trusted",
         covid_ownfaith == "Has not changed much" | covid_ownfaith == "Stronger" | covid_ownfaith == "Weaker") %>% 
  pivot_wider(names_from = covid_ownfaith, values_from = covid_change)
faith_table_wider

#I haven't used pivot_longer...not sure what to do with that here
```


```{r SimoneChunkCleaning}

characterize(pew)

#Setting up data and characterizing
sm_pew <- pew %>%
  mutate(covid_united = na_if(covid_united, 8),
         covid_united = na_if(covid_united, 9),
         covid_family = na_if(covid_family, 7),
         covid_family = na_if(covid_family, 8),
         covid_family = na_if(covid_family, 9))

sm_pew$country <- characterize(sm_pew$country)
sm_pew$sex <- characterize(sm_pew$sex)
sm_pew$covid_united <- characterize(sm_pew$covid_united)
sm_pew$covid_family <- characterize(sm_pew$covid_family) 

#Summary table of national unity percentages

sm_pew %>%
  select(country, covid_united) %>%
  tbl_summary(
    by = covid_united) 

#summary table of family closeness percentages

sm_pew %>%
  select(country, covid_family) %>%
  tbl_summary(
    by = covid_family)

# Figure for descriptive of changes in family closeness per country

sm_pew %>%
  select(country, covid_family)%>%
  drop_na(covid_family) %>%
  ggplot(aes(x = fct_infreq(country), fill=as.factor(covid_family))) +
  geom_bar() +
  theme_bw() +
  scale_fill_brewer(palette="spectral") +
  coord_flip() +
   labs(title = "Global Beliefs about Changes in Family Closeness Due to Covid",
       x = "Country",
       y = "Frequency", 
       fill = "Change in Family Closeness")

# Figure for descriptive of changes in perceptions of unity/division per country

sm_pew %>%
   select(country, covid_united)%>%
  drop_na(covid_united) %>%
  ggplot(aes(x = fct_infreq(country), fill=as.factor(covid_united))) +
  geom_bar() +
  theme_bw() +
  scale_fill_brewer(palette="spectral") +
  coord_flip() +
   labs(title = "Global Beliefs about Perceptions of National Unity or Division Due to Covid",
       x = "Country",
       y = "Frequency", 
       fill = "National Unity")


#Figure for global level of feelings of closeness to family due to COVID for those who feel country is more divided or united 

sm_pew %>%
   select(country, sex, covid_united, covid_family)%>%
  drop_na(covid_united, covid_family) %>%
  ggplot(aes(x = fct_reorder(country, covid_family), fill=as.factor(covid_family))) +
  geom_bar() +
  facet_wrap(~covid_united) +
  theme_bw() +
  scale_fill_brewer(palette="spectral") +
  coord_flip() +
   labs(title = "Global Beliefs about Changes in Family Closeness Due to Covid",
        subtitle = "Differences According to Perceptions of National Unity",
       x = "Country",
       y = "Frequency", 
       fill = "Change in Family Closeness") +
  theme(strip.text.x = element_text(size = 15, colour = "lightskyblue4")) +
  theme(strip.background =element_rect(fill="white"))


#Figure for level of belief about unity/division and perceptions of family closeness for men and women in the US

sm_pew %>%
   select(country, sex, covid_united, covid_family) %>%
  filter(country == "United States") %>%
  drop_na(covid_united, covid_family) %>%
  ggplot(aes(x = sex, fill=as.factor(covid_family))) +
  geom_bar(postion = "dodge") +
  facet_wrap(~covid_united) +
  theme_bw() +
  scale_fill_brewer(palette="spectral") +
   labs(title = "Beliefs about Changes to Family Closeness due to COVID in the US",
        subtitle = "Differences According to Perceptions of National Unity and Sex",
       x = "Sex",
       y = "Frequency", 
       fill = "Change in Family Closeness")

#Comparing USA and S Korea perceptions of Unity/division and family closeness due to covid (i.e. individualistic vs. more collectivistic)

sm_pew %>%
   select(country, covid_united, covid_family) %>%
  filter(country == "South Korea" | country == "United States") %>%
  drop_na(covid_united, covid_family) %>%
  ggplot(aes(x = country, fill=as.factor(covid_family))) +
  geom_bar() +
  facet_wrap(~covid_united) +
  theme_bw() +
  scale_fill_brewer(palette="spectral") +
   labs(title = "Beliefs about Changes to Family Closeness due to COVID in the USA vs. South Korea",
        subtitle = "Differences According to Perceptions of National Unity",
       x = "Country",
       y = "Frequency", 
       fill = "Change in Family Closeness") +
  theme(strip.text.x = element_text(size = 15, colour = "lightskyblue4")) +
  theme(strip.background =element_rect(fill="white"))


```

Introduction:
COVID-19 is an international health crisis that has been managed through various policies, including mask mandates, social distancing, remote work/schooling, etc., which have often disrupted people’s normal routines. The extent to which people have been affected by COVID-19 and subsequent interventions depends not only on the prevalence of infection, but also the substantive interventions to manage it. These, naturally, are related to each other, and subject to various factors, including country, population density, regionally empowered political party, and more. Because of the interplay of factors, there are numerous ways in which COVID-19 could affect perceptions of daily living, relationships (ranging from the level of interpersonal to international), religious beliefs, and so on. Thus, our research questions relate to perceived changes as a result of COVID-19. They are, 
1.	How does the COVID-19 Pandemic relate to perceptions of changes in daily life?;
2.	How has COVID-19 influenced beliefs about trust in others and religious beliefs?; and, 
3.	How has COVID-19 influenced beliefs about family closeness and national unity? 

Methods:
Participants
These data were collected by Pew Research Center, as part of their “Global Attitudes & Trends” Summer 2020 Questionnaire. Their recruitment procedure varied by country but generally employed a list-assisted Random Digit Dial (RDD) or both landlines and cell phones, stratified by region. Approximately 1000 responses per country were collected. A table of demographic data can be found in Table 1. Participants were age 18 or older, and were not compensated for their data.

Instrument
This questionnaire included 40 items. The number of items read to a respondent depended based on their country and response to prior questions.

